### 2017-07-07 introduction.tex
minor

While science has long been collaborative and data driven, today, more than ever before, researchers are dependent on the ability to safely store, effectively manage, and quickly analyze vast amounts of
data. Moreover, individual data-sets that are of interest to science and scholarship vary widely in size, often take on heterogeneous structures, and command varying levels of sensitivity. In fact, data sensitivity is often `custom' -defined specifically by
data use agreements that can be so granular as to vary from user to user and institution to institution. At the very same time, a typical research setting involves collaborators from multiple institutions that often share data, analysis techniques, and results. Yet, when data use agreements limit access and activities and these limits are imposed at the level of individual users, research collaboration can either lead to breaches of agreement or can grind to a halt under administrative burden when data is particularly sensitive.

>>>>

While science has long been collaborative and data driven, today, more than ever before, researchers are dependent on the ability to safely store, effectively manage, and quickly analyze vast amounts of
data. Moreover, individual data-sets that are of interest to science and scholarship vary widely in size, often take on heterogeneous structures, and command varying levels of sensitivity. In fact, data sensitivity is often `custom' -defined specifically by
data use agreements that can be so granular as to vary from user to user and institution to institution. At the very same time, however, a typical research setting involves collaborators from multiple institutions that often share data, analysis techniques, and results. This is, in fact, a cornerstone of modern research. Yet, when data are particularly sensitive and their use agreements limit access and activities at the level of individual users, research collaboration can either lead to inadvertent breaches of agreement or can grind to a halt under administrative burden.
